POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2024-01-27 existing-mechanisations/existing-mechanisations.tex
Make table of related mechanisations fit on page.
filled some entries in the table. Commented out some other which were not relevant or subsumed by previous ones

\item[\cite{Scagnetto2002}]               \url{https://doi.org/10.1016/S1571-0661(04)80507-3}

@@

\item[\cite{Miller2023}]                  \url{https://www.lix.polytechnique.fr/Labo/Dale.Miller/lProlog/examples/pi-calculus/toc.html}

@@

@@

\item[\cite{Watkins2008}]                 \url{https://doi.org/10.1016/j.entcs.2007.11.013}

@@

\item[\cite{Baelde2014}]                  \url{https://doi.org/10.6092/issn.1972-5787/4650}

@@

\item[\cite{Bengtson2007}]                \url{https://doi.org/10.1016/j.entcs.2007.08.017}

@@

@@

  \cite{Scagnetto2002}               & Coq                    &           &         &             &             \\

@@

  \cite{Miller2023}                  & Abella/$\lambda$Prolog &           &         &             &             \\

@@

  \cite{Despeyroux2000}              & Coq                    &           &         &             &             \\

@@

  \cite{Honsell2001}                 & Coq                    &           &         &             &             \\

@@

  \cite{Watkins2008}                 & CLF                    &           &         &             &             \\
  \cite{Tiu2010}                     & Bedwyr?                &           &         &             &             \\
  \cite{Cervesato2007}               & CLF                    &           &         &             &             \\
  \cite{Baelde2014}                  & Abella                 &           &         &             &             \\

@@

  \cite{Bengtson2007}                & Isabelle               &           & Nominal &             &             \\

@@

>>>>

\item[\cite{Honsell2001}]
% \item[\cite{Scagnetto2002}]
  \url{https://doi.org/10.1016/S1571-0661(04)80507-3} First weak HOAS
  formalization of the full pi calculus in Coq within the ``Theory of
  Context'', an axiomatic reflection of properties of
  names. Congruence properties of bisimilarity mainly via Park's
  principle.

@@

%\item[\cite{Miller2023}]                  \url{https://www.lix.polytechnique.fr/Labo/Dale.Miller/lProlog/examples/pi-calculus/toc.html}

@@

  weak HOAS encoding in Coq, no exotic terms. Proof of subject reduction.

@@

% \item[\cite{Watkins2008}]                 \url{https://doi.org/10.1016/j.entcs.2007.11.013}

@@

@@

% \item[\cite{Bengtson2007}]                \url{https://doi.org/10.1016/j.entcs.2007.08.017}

@@

\begin{center}
  \small

@@

  \cite{Honsell2001}               & Coq                    &           &weak HOAS + ToC         &cofix and Park's             & issues with cofix            \\

@@

  %\cite{Miller2023}                  & Abella/$\lambda$Prolog &           &         &             &             \\

@@

  \cite{Despeyroux2000}              & Coq                    &           & weak HOAS         &             &             \\

@@

@@

%  \cite{Watkins2008}                 & CLF                    &           &         &             &             \\
  \cite{Tiu2010}                     & Abella                &           & HOAS + $\nabla$        & coDefine             &              \\
  \cite{Cervesato2007}               & CLF                    &           & HOAS + substructural opsem       &             &   no metatheory          \\

@@

%  \cite{Bengtson2007}                & Isabelle               &           & Nominal &             &             \\

@@

\end{center}
